---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# frogs

Data from the Calaveras Jumping Frog Jubilee, as collected for this paper by
Astley et al (proper citation coming, on an airplane!): Chasing maximal
performance: a cautionary tale from the celebrated jumping frogs of Calaveras
County.

DATA IS NOT CLEANED YET! Still under development.

## Installation

You can install frogs from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jennybc/frogs")
```

## Getting to know the frogs

At this point, all we know is that each row is one frog-jump. Frog ids coming ...

```{r}
library(frogs)
library(tidyverse)

frogs
glimpse(frogs)
```

An early figure. Do frogs need to warm up? Do they fatigue? Yes and yes.

```{r frog-fatigue, echo = FALSE}
frogs2 <- frogs %>% 
  filter(jump_n < 7) %>% 
  mutate(
    jump_n = as.factor(as.integer(jump_n))
  )
ggplot(frogs2, aes(x = distance, color = jump_n)) +
  geom_density()
```

